Beyoncé

### 2024-04-15 paper/paper.qmd
Fix some minor typos

library(tidyverse)
library(rstanarm)
library(knitr)
library(here)
library(ggplot2)
library(arrow)
library(scales)
library(modelsummary)
library(marginaleffects)
library(broom.mixed)

@@

We analyzed the data in R [@citeR] using the following packages: `arrow` [@arrow], `broom.mixed` [@broommixed], `ggplot2` [@ggplot2], `here` [@here], `janitor` [@janitor], `kable` [@kable], `knitr` [@knitr], `marginaleffects` [@marginaleffects], `modelsummary` [@modelsummary], `rstanarm` [@rstanarm], `scales` [@scales], and `tidyverse` [@tidyverse].

>>>>

library(arrow)
library(broom.mixed)
library(ggplot2)
library(here)
library(knitr)
library(marginaleffects)
library(modelsummary)
library(rstanarm)
library(tidyverse)

@@

We analyzed the data in R [@citeR] using the following packages: `arrow` [@arrow], `broom.mixed` [@broommixed], `ggplot2` [@ggplot2], `here` [@here], `janitor` [@janitor], `knitr` [@knitr], `marginaleffects` [@marginaleffects], `modelsummary` [@modelsummary], `rstanarm` [@rstanarm], and `tidyverse` [@tidyverse].
